The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-07-15 src/science/paper.tex
Hardcode bib to paper.

\bibliography{bibliography}

\bibliographystyle{Science}

>>>>

\begin{thebibliography}{10}

\bibitem{Mathieu2021}
E.~Mathieu, {\it et~al.\/}, {\it Nature Human Behaviour\/}  (2021).

\bibitem{Contreras2021}
S.~Contreras, {\it et~al.\/}, {\it arXiv\/}  (2021).

\bibitem{Mina2021}
M.~J. Mina, K.~G. Andersen, {\it Science\/} {\bf 371}, 126 (2021).

\bibitem{Aleta2020}
A.~Aleta, {\it et~al.\/}, {\it Nature Human Behaviour\/} {\bf 4}, 964 (2020).

\bibitem{Hinch2020}
R.~Hinch, {\it et~al.\/}, {\it medRxiv\/}  (2020).

\bibitem{Mossong2008}
J.~Mossong, {\it et~al.\/}, {\it PLoS medicine\/} {\bf 5} (2008).

\bibitem{Hoang2019}
T.~Hoang, {\it et~al.\/}, {\it Epidemiology\/} {\bf 30}, 723 (2019).

\bibitem{Lessler2021}
J.~Lessler, {\it et~al.\/}, {\it Science\/} {\bf 372}, 1092 (2021).

\bibitem{Cheng2021}
Y.~Cheng, {\it et~al.\/}, {\it Science\/}  (2021).

\bibitem{Jones2021}
T.~C. Jones, {\it et~al.\/}, {\it Science\/}  (2021).

\bibitem{Hunter2021}
P.~R. Hunter, J.~Brainard, {\it medRxiv\/}  (2021).

\bibitem{LevineTiefenbrun2021}
M.~Levine-Tiefenbrun, {\it et~al.\/}, {\it Nature medicine\/} {\bf 27}, 790
  (2021).

\bibitem{Petter2021}
E.~Petter, {\it et~al.\/}, {\it medRxiv\/}  (2021).

\bibitem{Pritchard2021}
E.~Pritchard, {\it et~al.\/} .

\bibitem{Bruemmer2021}
L.~E. Br\"{u}mmer, {\it et~al.\/}, {\it medRxiv\/}  (2021).

\bibitem{Smith2021}
R.~L. Smith, {\it et~al.\/}, {\it The Journal of Infectious Diseases\/}
  (2021). Jiab337.

\bibitem{McFadden1989}
D.~McFadden, {\it Econometrica: Journal of the Econometric Society\/} pp.
  995--1026 (1989).

\bibitem{Hale2020}
T.~Hale, {\it et~al.\/}, {\it Blavatnik School of Government\/}  (2020).

\bibitem{Shapley2016}
L.~S. Shapley, {\it 17. A value for n-person games\/} (Princeton University
  Press, 2016).

\bibitem{Gavenciak2021}
T.~Gaven{\v c}iak, {\it et~al.\/}, {\it medRxiv\/}  (2021).

\bibitem{Fetzer2021}
T.~Fetzer, T.~Graeber, {\it Forthcoming, Proceedings of the National Academy of
  Sciences\/}  (2021).

\bibitem{Kretzschmar2020}
M.~E. Kretzschmar, {\it et~al.\/}, {\it The Lancet Public Health\/} {\bf 5},
  e452 (2020).

\bibitem{Dorn2020b}
F.~Dorn, {\it et~al.\/}, {\it ifo Schnelldienst\/} {\bf 73}, 29 (2020).

\bibitem{StillmanTonin2021}
S.~Stillman, M.~Tonin, Communities and testing for {COVID-19} (2021). IZA
  Discussion Paper No. 14012.

\bibitem{KochInstitut2021a}
{Robert Koch-Institut}, Corona-monitoring bundesweit (rki-soep-studie), {\it
  Tech. rep.\/}, {Robert Koch-Institut} (2021).

\end{thebibliography}
